---
title: "assignment2Solution_s3879312"
author: "Thu Tran"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r import libraries}
rm(list=ls()) 
library(TSA)
library(tseries)
library(ggplot2)
library(lmtest)
library(forecast)
```


```{r data overview}
# read data into a data frame
arctic_sea_ice <- read.csv("assignment2Data2023.csv", header = TRUE)
# display first 3 rows of data frame
head(arctic_sea_ice, n=3)
# class of the data
class(arctic_sea_ice)
# display summary statistics
summary(arctic_sea_ice)
```


```{r Create the ACF plot for finding the frequency - no need since this is annual data}
# Create the ACF plot with custom title, y-axis label, x-axis label, and color
acf(arctic_sea_ice, main = "ACF of Arctic Sea Ice Extent")
# confirm the frequency
frequency(arctic_sea_ice)
```


```{r convert data frame to time series (ts) object}
# Create a vector of the Arctic sea ice minimum extent values
arctic_sea_ice_ts <- arctic_sea_ice$Arctic.Sea.Ice.Extent..million.square.km.
# Convert the vector to a time series object
arctic_sea_ice_ts <- ts(arctic_sea_ice_ts, start = 1979, end = 2022, frequency = 1)
class(arctic_sea_ice_ts)
arctic_sea_ice_ts
```


```{r time series plot}
plot(arctic_sea_ice, type='o', main = "Time series plot of Arctic Sea Ice Minimum Extent (1979-2022)", ylab = "Million square km", xlab = "Year", col="blue")
```

```{r normality test of the original time series data}
qqnorm(y = arctic_sea_ice_ts, main = "QQ plot of the Acrtic Extent series", col = "blue")
qqline(y = arctic_sea_ice_ts, col = 2, lwd = 1, lty = 2)
shapiro.test(arctic_sea_ice_ts)
# p-value = 0.0373 
```



```{r scatter plot to show the relationship between pairs of consecutive Arctic Sea Ice Minimum Extent}
plot(y=arctic_sea_ice_ts,x=zlag(arctic_sea_ice_ts),ylab='Million square km', xlab='Previous Year Arctic Sea Ice Minimum Extent (million square km)', main = "Scatter plot of Arctic Sea Ice Minimum Extent in consequtive years", col="blue")

# the correlation show linear relationship between pairs of consecutive Arctic Sea Ice Minimum Extent
y = arctic_sea_ice_ts             # Read the annual data into y
x = zlag(arctic_sea_ice_ts)       # Generate first lag of the annual series
index = 2:length(x)    # Create an index to get rid of the first NA value in x
cor(y[index],x[index]) # Calculate correlation between numerical values in x and y
```



```{r Stationary Check: ACF plot and ACF numerical representation}
# Create the ACF plot: slowly decay trend
acf(arctic_sea_ice_ts, main = "ACF of Arctic Sea Ice Extent Time Series")

# convert the ACF plot into a numerical representation
# Calculate ACF values for the Arctic Sea Ice Extent Time Series
acf_values <- acf(arctic_sea_ice_ts, plot = FALSE)
# Print the ACF values
acf_values$acf
```


```{r Stationary Check: PACF plot and PACF numerical representation}
# large first lag in the pacf
pacf(arctic_sea_ice_ts, main = "PACF of Arctic Sea Ice Minimum Extent Time Series")

# convert the ACF plot into a numerical representation
# Calculate PACF values for the Arctic Sea Ice Minimum Extent Time Series
pacf_values <- pacf(arctic_sea_ice_ts, plot = FALSE)
# Print the PACF values
pacf_values$acf
```

```{r Stationary Check: of the original time series data}
adf.test(arctic_sea_ice_ts)
# p-value = 0.4433: non-stationary
```




```{r Box-Cox transformation}
BC <- suppressWarnings(BoxCox.ar(y = arctic_sea_ice_ts, lambda = seq(-2, 2, 0.01)))
title(main = "Log-likelihood versus the values of lambda for Acrtic Extent")

BC$ci # Values of the first and third vertical lines

# To find the lambda value of the middle vertical line
lambda <- BC$lambda[which(max(BC$loglike) == BC$loglike)]
lambda
```


```{r}
# Apply Box-Cox transformation using the optimal lambda value 
BC_arctic_sea_ice_ts <- ((arctic_sea_ice_ts^lambda) - 1) / lambda

# Set the output file and dimensions (width, height) in pixels
png("BC_arctic_sea_ice_ts.png", width = 1200, height = 600)

# Set up the layout for side-by-side plots
par(mfrow = c(1, 2))

# Create a time series plot of the original data
plot(arctic_sea_ice_ts,
     type = "l",
     col = "black",
     main = "Original Arctic Sea Ice Minimum Extent Time Series",
     xlab = "Year",
     ylab = "Arctic Sea Ice Minimum Extent (million square km)")

# Create a time series plot of the Box-Cox transformed data
plot(BC_arctic_sea_ice_ts,
     type = "l",
     col = "blue",
     main = "Box-Cox transformation Arctic Sea Ice Minimum Extent Time Series",
     xlab = "Year",
     ylab = "Box-Cox transformation Arctic Sea Ice Minimum Extent (million square km)")

# Reset the layout
par(mfrow = c(1, 1))
```

```{r Transformation improve normality?}
qqnorm(y = BC_arctic_sea_ice_ts, main = "QQ plot of the Acrtic Extent series", col = "blue")
qqline(y = BC_arctic_sea_ice_ts, col = 2, lwd = 1, lty = 2)
shapiro.test(BC_arctic_sea_ice_ts)
```


```{r First Difference}  
# First Difference 
first_diff_arctic_sea_ice <- diff(arctic_sea_ice_ts, differences = 1)

# Set the output file and dimensions (width, height) in pixels
png("first_differenced_arctic_sea_ice_plot.png", width = 1200, height = 600)
# Set up the layout for side-by-side plots
par(mfrow = c(1, 2))
# Create a time series plot of the original data
plot(arctic_sea_ice_ts,
     type = "l",
     col = "black",
     main = "Original Arctic Sea Ice Minimum Extent Time Series",
     xlab = "Year",
     ylab = "Arctic Sea Ice Minimum Extent (million square km)")
# Create a time series plot of the first differenced data
plot(first_diff_arctic_sea_ice,
     type = "l",
     col = "blue",
     main = "First Differenced Arctic Sea Ice Minimum Extent Time Series",
     xlab = "Year",
     ylab = "Differenced Arctic Sea Ice Minimum Extent (million square km)")
# Reset the layout
par(mfrow = c(1, 1))
```


```{r Stationary Tests}
suppressWarnings({
  adf <- adf.test(first_diff_arctic_sea_ice, alternative = "stationary")
  pp <- pp.test(first_diff_arctic_sea_ice)
  kpss <- kpss.test(first_diff_arctic_sea_ice, null = "Level")
})

# Print the test results without the warnings
adf
pp
kpss
```


```{r}
# Plot the ACF of the first differenced time series
acf(first_diff_arctic_sea_ice, main = "ACF of the First Difference")
# Plot the PACF of the first differenced time series
pacf(first_diff_arctic_sea_ice, main = "PACF of the First Difference")
# {ARIMA(1,1, 1), ARMA(2,1,1), ARMA(2,1,2), ARMA(3,1,1), ARMA(3,1,2)}
```



```{r Model Selection: EACF table}
# EACF
eacf(first_diff_arctic_sea_ice, ar.max = 10, ma.max = 10)
# {ARIMA(0,1,1), ARIMA(0,1,2), ARIMA(1,1,1), ARIMA(1,1,2)}
```

```{r BIC Table}
res = armasubsets(y=first_diff_arctic_sea_ice,nar=10,nma=10,y.name='p',ar.method='ols')
plot(res)
# {ARIMA(1,1,9), ARIMA(6,1,9)}
```



```{r Model Fitting Parameter Estimations, BIC and AIC scores}
fit_arima_models <- function(time_series, arima_orders) {
  models <- list()
  for (order in arima_orders) {
    model <- arima(time_series, order = order, method = 'CSS-ML')
    coef_test <- coeftest(model)
    aic_score <- AIC(model)
    bic_score <- BIC(model)
    models[[paste("ARIMA(", paste(order, collapse = ","), ")", sep = "")]] <- list(model = model, coef_test = coef_test, AIC = aic_score, BIC = bic_score)
  }
  return(models)
}

# Define the list of ARIMA models
arima_orders <- list(
  c(1, 1, 1), c(2, 1, 1), c(2, 1, 2), c(3, 1, 1), c(3, 1, 2),
  c(0, 1, 1), c(0, 1, 2), c(1, 1, 1), c(1, 1, 2),
  c(1, 1, 9), c(6, 1, 9)
)
arctic_sea_ice_models <- fit_arima_models(arctic_sea_ice_ts, arima_orders)

# Accessing the models and their coefficient tests, AIC and BIC scores:
for (model_name in names(arctic_sea_ice_models)) {
  cat("Model:", model_name, "\n")
  cat("Coefficient test:\n")
  print(arctic_sea_ice_models[[model_name]]$coef_test)
  cat("AIC:", arctic_sea_ice_models[[model_name]]$AIC, "\n")
  cat("BIC:", arctic_sea_ice_models[[model_name]]$BIC, "\n\n")
}
```

```
``

```{r "ME", "RMSE", "MAE", "MPE", "MAPE", "MASE", "ACF1" scores}
# Function to fit ARIMA models and compute accuracy
fit_arima_models <- function(data, arima_orders) {
  models <- list()
  accuracy_measures <- list()
  
  for (order in arima_orders) {
    model <- Arima(data, order = order, method = 'CSS-ML')
    models[[paste0("ARIMA(", paste(order, collapse = ","), ")")]] <- model
    accuracy_measures[[paste0("ARIMA(", paste(order, collapse = ","), ")")]] <- accuracy(model)[1:7]
  }
  
  df_accuracy <- data.frame(do.call(rbind, accuracy_measures))
  colnames(df_accuracy) <- c("ME", "RMSE", "MAE", "MPE", "MAPE", "MASE", "ACF1")
  
  return(df_accuracy)
}

# Define the list of ARIMA models
arima_orders <- list(
  c(1, 1, 1), c(2, 1, 1), c(2, 1, 2), c(3, 1, 1), c(3, 1, 2),
  c(0, 1, 1), c(0, 1, 2), c(1, 1, 1), c(1, 1, 2),
  c(1, 1, 9), c(6, 1, 9)
)

# Call the function with your data and the list of ARIMA models
accuracy_results <- fit_arima_models(arctic_sea_ice_ts, arima_orders)
print(accuracy_results)

```



# We found ARIMA(1,1,2) model is the most promissing one for Diagnostic Checking

```{r 4 residual plots}
# Fit the ARIMA model
model.112.CSSML <- arima(arctic_sea_ice_ts, order = c(1, 1, 2), method = 'CSS-ML')
model.112.CSSMLRes <- rstandard(model.112.CSSML)

# Set up the multi-panel plot layout
par(mfrow = c(2, 2))

# Time series plot of standardized residuals
plot(model.112.CSSMLRes, xlab = 'Time', ylab = 'Standardized Residuals', type = 'o',
     main = "Time series plot of standardized residuals", col = "blue")

# Histogram of standardized residuals
hist(model.112.CSSMLRes, ylab = 'Standardized Residuals',
     main = "Histogram of standardized residuals", col = "blue")

# QQ plot of standardized residuals
qqnorm(model.112.CSSMLRes, main = "QQ plot of standardized residuals.", col = "blue")
qqline(model.112.CSSMLRes, col = 2, lwd = 1, lty = 2)

# ACF plot of standardized residuals
acf(model.112.CSSMLRes, main = "ACF plot of standardized residuals.")

```



```{r autocorrelation test}
Box.test(model.112.CSSMLRes, type = "Ljung-Box")
```

```{r normality test}
shapiro.test(model.112.CSSMLRes)
```


```{r Forecasting consecutive 10 years}
model.112.CSSMLA = Arima(arctic_sea_ice_ts,order=c(1,1,2),method='CSS-ML')
model.112.CSSMLAfrc = forecast::forecast(model.112.CSSMLA, h = 10)
plot(model.112.CSSMLAfrc)
model.112.CSSMLAfrc
```

